### 2018-11-04 Sections/cryptowars.tex
QKD attack and shallow circuits sections

>>>>

In general, Eve will probe into the optical channel that Alice and Bob use to communicate. She send her own states into Alice’s system, which will reflect off the same apparatus Alice uses used to encode her signal. Eve's states can be imprinted upon some information about the encoding used by Alice, when Eve measures them. She can then use the result of this measurement, combined with some operation on the Alice's signals to make a best estimate of the quantum state that Alice sent to Bob, thus giving her some non-negligible information mutual with the key\cite{PhysRevA.97.042335}.

### 2018-11-04 Sections/quantum_algorithms.tex
adding braket package
QKD attack and shallow circuits sections

>>>>

\subsection{Quantum advantage with shallow circuits}\index{shallow_circuits}

% Good reasons for thinking that quantum computers have capabilities surpassing classical computers. Preskill - three reasons

% Additional area evidence - quiry complexity:
% A blackbox $U_\ell$
% \begin{align}
% \ket{x}-\rightarrow U_l -\rightarrow (-1)^{z\cot x} \ket{x}
% \end{align}

% A linear Boolean function is parametrized by $z$, a hidden string $in \{0,1\}^n$. The goal
% is to extract $z$.

% In the quantum case - the blackbox/oracle simply a unitary which computes the function
% into the phase.

% A provable, non-oracular quantum speed up.

% Constant-depth circuits - (definition). Assume the input is classical, input is classical, output is by measuring in computational basis.

% Deep circuits: few qubits -> classically simulable.

% Shallow circuits -> many qubits -> potential for quantum advantage.

% 
% Classical circuit
% \begin{align}
% f:{0,1}^k-> \{0,1 \}
% \end{align}
% initial bits can be copied into multiple locations, unlike the quantum. number of input bits k called fan in. Consider bounded fanin gates. Allow the circuit to be probabilistic (provided random bits give).

% The problem is solved with certainty by a constant-depth quantum circuit.

As we discuss in Sec.~\ref{sec:NISQ}, we have good reasons to believe that quantum computer
have super-classical abilities. Recently, an unconditional proof of a quantum speed-up has
been shown for a class of circuits.

Motivation: it is incredibly difficult to compare quantum VS classical polynomial time computation, with a significant implication: this would separate BPP from BQP.
Given that currently we have noisy gates, with $n$ qubits, depth $d$, and an error rate $\epsilon$. Intuitively, we need the condition
\begin{align}
nd<<1/\epsilon
\end{align}
\noindent to hold, in order for a quantum algorithm to run successfully. If $d$ is large, then noise dominates and our circuit is classically simulable; on the other hand, if we have a large $n$ and small $d$ (constant depth circuits), we may observe a quantum speed up in the near future.
Now we will see that there is a distinction between constant depth circuits run using classical VS quantum algorithm.

\color{blue}
The result is for the following hidden linear function (HLF) problem. Given an 
$n\times n$ symmetric binary matrix $A$, we specify a quadratic form
\begin{align}
q(x) = \vec x^T A \vec x \text{(mod 4)}.
\end{align}
\noindent The goal is to find a binary vector $\vec z \in {0,1}^n$ such that
% 
\begin{align}
q(x) = 2 \vec z^T \hat x
\end{align}
\noindent for all $\vec x$ in the binary null-space of A.

The quantum alvorithm that solves the 2D HLF problem is similar to the Bernstein and Vazirani \cite{}. A quantum circuit $U_q$ acts on the basis state $\vec x \in \{ 0,1\}^n$
\begin{align}
U_q \ket{x} = i^{q(x)} \ket{x}
\end{align}
The solution is obtained by measuring the state $\ket{\Psi_q}$ in the computational basis,
\begin{align}
\ket{\Psi_q} &= H^{\otimes n }U_q H^{\otimes n} \ket{0}^{\otimes n} \\
&= \frac{1}{2^n}\sum_{\vec x,\vec z \in \{ 0,1\}^n} i^{q(x)} (-1)^{\vec z^T x}\ket{z}
\end{align}
\noindent where $H$ is the Hadamard gate. A schematic of the circuit is given in Fig~.\ref{fig:2DHLF}.
Destructive interference between terms in x results a vanishing amplitude
$\braket{z|\Psi_q}=0$ on basis state $\ket{z}$ which are not solutions of the HLF problem.
The circuit $U_q$ can be decomposed into a product of CZ gates and phase-shift gates 
\begin{align}
S_i = \begin{pmatrix}
    1 & 0\\
    0 & -i
    \end{pmatrix}
\end{align}

\begin{figure}[h]
\includegraphics[trim = 0cm 0cm 0cm 0cm, clip, width=1.0\linewidth]{2DHLFcircuit.pdf}
\caption{\label{fig:2DHLF} Quantum circuit to solve the 2D HLF problem. }
\end{figure}

If we lay out the circuit in 2D (hence the 2D HLF problem),it only requires classically controlled Clifford gates between nearest neighbor qubits on a 2D grid. For an example, see Fig.~\ref{fig:2DHLFgrid}.
\begin{figure}[h]
\includegraphics[trim = 0cm 0cm 0cm 0cm, clip, width=0.8\linewidth]{2DHLF_grid.jpg}
\caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid.}
\end{figure}

Now, comparing the quantum algorithm to a classical one, it has been proven that any probabilistic classical circuit with bounded input that solves the 2D HLF problem with high probability $\epsilon \leq 1/8$ must have depth increasing logarithmically with input size\cite{}. The speed-up here is provided by quantum non-locality. 
% 
The fact that a problem can be solved with constant depth quantum circuits, but not classical ones shows that there is a clear separation in computational speed between the two cases.

\color{black}
